Numerical experiment investigating the influence of drag on trajectory patterns of floating macroalgae

### 2021-05-04 thesis_chapter_3.Rmd
final corrections for chapter 3

---
title: 'Numerical experiment investigating the influence of drag on trajectory patterns of floating macroalgae'
author: 
- R Coppin^[University of the Western Cape], C Rautenbach^[National Institute of Water and Atmospheric Research], AJ Smit^[University of the Western Cape South African Observation Network]
output:
  word_document:
    reference_docx: markdown/template.docx
  pdf_document:
    fig_caption: yes
    latex_engine: xelatex
  html_document:
bibliography: references.bib
csl: markdown/frontiers.csl.txt
abstract: "**Abstract**: Ocean currents act as an important dispersal mechanism of material on the ocean surface, both natural and anthropogenic. Macroalgae are one of the most important natural dispersal vectors and are regarded as the 'tumble-weed' of the ocean. Despite many studies that exist on the topic, the relative role of wind and surface currents in influencing the trajectory of macroalgal dispersal is still unknown. Past studies focus on kelp-rafts, which can vary greatly in size, making it difficult to form a consenses as to the relative role of wind versus surface currents. In addition, past studies have not considered surface-area in relation to drag characteristics of floating macroalgae, both of which have been shown to play a role in the trajectory and accumulation of other flotsam. Advances in Lagrangian trajectory modeling have been rapid in recent years and allow the use of numerical experiments to investigate trajectories of flotsam in the ocean. This study aimed to shed light on the relative role of wind versus surface currents, and the role of drag in macrolagal trajectory and accumulation. We focused on solitary kelp individuals. This was achieved by comparing simulations of virtual kelp 'particles' which incorporate drag with that of purely Lagrangian particles. The results showed that the virtual kelp particles do follow the ocean currents in general, but that the inclusion of drag into the scenarios causes accumulation in eddys within the study domain. The results also point to the importance of sub-mesoscale features, such as eddys, as important surface accumulation zones for solitary floating macroalage."
---

@@

waterdrag_plot <- ggplot()+
  geom_polygon(data = south_africa_coast_hi_res, aes(x = lon, y = lat, group = PID), size = 1.0, colour = "black",     fill = "grey") +
  coord_cartesian(xlim = c(8, 28), ylim = c(-38, -26)) +
  geom_path(data = total_mean_water, aes(x = lon, y = lat, colour = type))+
  xlab("Longtitude") + 
  ylab("Latitude") + 
  ggtitle("") +
  scale_colour_discrete("Type") +  
  coord_fixed(ratio=1/1) + # fix the aspect ratio of plot
  theme(plot.title = element_text(hjust = 0.5)) +
  theme_bw()

wwdrag_plot <- ggplot()+
  geom_polygon(data = south_africa_coast_hi_res, aes(x = lon, y = lat, group = PID), size = 1.0, colour = "black",     fill = "grey") +
  coord_cartesian(xlim = c(8, 28), ylim = c(-38, -26)) +
  geom_path(data = total_mean_ww, aes(x = lon, y = lat, colour = type))+
  xlab("Longtitude") + 
  ylab("Latitude") + 
  ggtitle("") +
  scale_colour_discrete("Type") +  
  coord_fixed(ratio=1/1) + # fix the aspect ratio of plot
  theme(plot.title = element_text(hjust = 0.5)) +
  theme_bw()

@@

waterdrag_plot_April <- ggplot()+
  geom_polygon(data = south_africa_coast_hi_res, aes(x = lon, y = lat, group = PID), size = 1.0, colour = "black",     fill = "grey") +
  coord_cartesian(xlim = c(8, 28), ylim = c(-38, -26)) +
  geom_path(data = total_mean_water_April, aes(x = lon, y = lat, colour = type))+
  xlab("Longtitude") + 
  ylab("Latitude") + 
  ggtitle("") +
  scale_colour_discrete("Type") +  
  coord_fixed(ratio=1/1) + # fix the aspect ratio of plot
  theme(plot.title = element_text(hjust = 0.5)) +
  theme_bw()

wwdrag_plot_April <- ggplot()+
  geom_polygon(data = south_africa_coast_hi_res, aes(x = lon, y = lat, group = PID), size = 1.0, colour = "black",     fill ="grey") +
  coord_cartesian(xlim = c(8, 28), ylim = c(-38, -26)) +
  geom_path(data = total_mean_ww_April, aes(x = lon, y = lat, colour = type))+
  xlab("Longtitude") + 
  ylab("Latitude") + 
  ggtitle("") +
  scale_colour_discrete("Type") +  
  coord_fixed(ratio=1/1) + # fix the aspect ratio of plot
  theme(plot.title = element_text(hjust = 0.5)) +
  theme_bw()

@@

waterdrag_plot_July <- ggplot()+
  geom_polygon(data = south_africa_coast_hi_res, aes(x = lon, y = lat, group = PID), size = 1.0, colour = "black",     fill = "grey") +
  coord_cartesian(xlim = c(8, 28), ylim = c(-38, -26)) +
  geom_path(data = total_mean_water_July, aes(x = lon, y = lat, colour = type))+
  xlab("Longtitude") + 
  ylab("Latitude") + 
  ggtitle("") +
  scale_colour_discrete("Type") + 
  coord_fixed(ratio=1/1) + # fix the aspect ratio of plot
  theme(plot.title = element_text(hjust = 0.5)) +
  theme_bw()

wwdrag_plot_July <- ggplot()+
  geom_polygon(data = south_africa_coast_hi_res, aes(x = lon, y = lat, group = PID), size = 1.0, colour = "black",     fill = "grey") +
  coord_cartesian(xlim = c(8, 28), ylim = c(-38, -26)) +
  geom_path(data = total_mean_ww_July, aes(x = lon, y = lat, colour = type))+
  xlab("Longtitude") + 
  ylab("Latitude") + 
  ggtitle("") +
  scale_colour_discrete("Type") +  
  coord_fixed(ratio=1/1) + # fix the aspect ratio of plot
  theme(plot.title = element_text(hjust = 0.5)) +
  theme_bw()

@@

waterdrag_plot_Oct <- ggplot()+
  geom_polygon(data = south_africa_coast_hi_res, aes(x = lon, y = lat, group = PID), size = 1.0,     colour = "black",     fill = "grey") +
  coord_cartesian(xlim = c(8, 28), ylim = c(-38, -26)) +
  geom_path(data = total_mean_water_Oct, aes(x = lon, y = lat, colour = type))+
  xlab("Longtitude") + 
  ylab("Latitude") + 
  ggtitle("") +
  scale_colour_discrete("Type") +  
  theme(plot.title = element_text(hjust = 0.5)) +
  coord_fixed(ratio=1/1) + # fix the aspect ratio of plot
  theme_bw()

wwdrag_plot_Oct <- ggplot() +
  geom_polygon(data = south_africa_coast_hi_res, aes(x = lon, y = lat, group = PID), size = 1.0,     colour = "black",     fill = "grey") +
  coord_cartesian(xlim = c(8, 28), ylim = c(-38, -26)) +
  geom_path(data = total_mean_ww_Oct, aes(x = lon, y = lat, colour = type))+
  xlab("Longtitude") + 
  ylab("Latitude") + 
  ggtitle("") +
  scale_colour_discrete("Type") +  
  guides(fill=guide_legend(title="Number of particles")) +
  theme(plot.title = element_text(hjust = 0.5)) +
  coord_fixed(ratio=1/1) + # fix the aspect ratio of plot
  theme_bw()

@@

```{r echo=FALSE, message=FALSE, warning=FALSE, fig.height=10, fig.width=7.5, fig.cap="Figure 3: Comparison of mean trajectories. Simulations of hydrodynamic drag are presented in Panels A, C, E, G for January, April, July, and October, respectively. Results of simulations including both hydrodynamic drag and wind are in Panels B, D, F, H for January, April, July, and October, respectively. In all panels the passive simulations are represented by black lines."}

@@

heatmap_RK4_acc <- ggplot() +
  geom_polygon(data = south_africa_coast_hi_res, aes(x = lon, y = lat, group = PID),
               size = 1.0, colour = "black", fill = NA) +
  #geom_bin2d(data = p_RK4, bins = 80, aes(x = lon, y = lat)) +
  geom_hex(data = pass_acc, bins = 80, aes(x = lon, y = lat), legend = FALSE) +  scale_fill_continuous(type = "viridis", limits = c(1, 720)) +
  geom_path(data = pass_acc_mean,aes(x = lon, y = lat, color = 'red'), show.legend = FALSE) +
  coord_cartesian(xlim = c(14, 20), ylim = c(-35, -30)) +
  xlab("Longtitude") +
  ylab("Latitude") +
  ggtitle("Passive particles") +
  guides(fill=guide_legend(title="Number of particles")) +
  coord_fixed(ratio=1/1) + # fix the aspect ratio of plot
  theme_bw() +
  theme(plot.title = element_text(hjust = 0.5))

heatmap_kelp_acc <- ggplot() +
  geom_polygon(data = south_africa_coast_hi_res, aes(x = lon, y = lat, group = PID),
               size = 1.0, colour = "black", fill = NA) +
  #geom_bin2d(data = p_RK4, bins = 80, aes(x = lon, y = lat)) +
  geom_hex(data = kelp_acc, bins = 80, aes(x = lon, y = lat), legend = FALSE) +  scale_fill_continuous(type = "viridis", limits = c(1, 720)) +
  geom_path(data = kelp_acc_mean,aes(x = lon, y = lat, color = 'red'), show.legend = FALSE) +
  coord_cartesian(xlim = c(14, 20), ylim = c(-35, -30)) +
  xlab("Longtitude") +
  ylab("Latitude") +
  ggtitle("Kelp particles") +
  guides(fill=guide_legend(title="Number of particles")) +
  coord_fixed(ratio=1/1) + # fix the aspect ratio of plot
  theme_bw() +
  theme(plot.title = element_text(hjust = 0.5))

point_RK4_acc <- ggplot() +
  geom_polygon(data = south_africa_coast_hi_res, aes(x = lon, y = lat, group = PID),
               size = 1.0, colour = "black", fill = NA) +
  geom_point(data = pass_acc, aes(x = lon, y = lat, colour = distance)) +
  coord_cartesian(xlim = c(14, 20), ylim = c(-35, -30)) +
  xlab("Longtitude") +
  ylab("Latitude") +
  ggtitle("") +
  guides(fill=guide_legend(title="Number of particles")) +
  coord_fixed(ratio=1/1) + # fix the aspect ratio of plot
  theme_bw() +
  theme(plot.title = element_text(hjust = 0.5))

point_kelp_acc <- ggplot() +
  geom_polygon(data = south_africa_coast_hi_res, aes(x = lon, y = lat, group = PID),
               size = 1.0, colour = "black", fill = NA) +
  geom_point(data = kelp_acc, aes(x = lon, y = lat, colour = age)) +
  #scale_fill_continuous(type = "viridis", limits = c(0, 30)) +
  coord_cartesian(xlim = c(14, 20), ylim = c(-35, -30)) +
  xlab("Longtitude") +
  ylab("Latitude") +
  ggtitle("") +
  guides(fill=guide_legend(title="Age")) +
  coord_fixed(ratio=1/1) + # fix the aspect ratio of plot
  theme_bw() +
  theme(plot.title = element_text(hjust = 0.5))

@@

heatmap_RK4_acc_April <- ggplot() +
  geom_polygon(data = south_africa_coast_hi_res, aes(x = lon, y = lat, group = PID),
               size = 1.0, colour = "black", fill = NA) +
  #geom_bin2d(data = p_RK4, bins = 80, aes(x = lon, y = lat)) +
  geom_hex(data = pass_acc_April, bins = 80, aes(x = lon, y = lat), legend = FALSE) +  scale_fill_continuous(type = "viridis", limits = c(1, 720)) +
  geom_path(data = pass_acc_mean_April, aes(x = lon, y = lat, color = 'red'), show.legend = FALSE) +
  coord_cartesian(xlim = c(14, 20), ylim = c(-35, -30)) +
  xlab("Longtitude") +
  ylab("Latitude") +
  ggtitle("Passive particles") +
  guides(fill=guide_legend(title="Number of particles")) +
  coord_fixed(ratio=1/1) + # fix the aspect ratio of plot
  theme_bw() +
  theme(plot.title = element_text(hjust = 0.5))

heatmap_kelp_acc_April <- ggplot() +
  geom_polygon(data = south_africa_coast_hi_res, aes(x = lon, y = lat, group = PID),
               size = 1.0, colour = "black", fill = NA) +
  #geom_bin2d(data = p_RK4, bins = 80, aes(x = lon, y = lat)) +
  geom_hex(data = kelp_acc_April, bins = 80, aes(x = lon, y = lat), legend = FALSE) +  scale_fill_continuous(type = "viridis", limits = c(1, 720)) +
  geom_path(data = kelp_acc_mean_April,aes(x = lon, y = lat, color = 'red'), show.legend = FALSE) +
  coord_cartesian(xlim = c(14, 20), ylim = c(-35, -30)) +
  xlab("Longtitude") +
  ylab("Latitude") +
  ggtitle("Kelp particles") +
  guides(fill=guide_legend(title="Number of particles")) +
  coord_fixed(ratio=1/1) + # fix the aspect ratio of plot
  theme_bw() +
  theme(plot.title = element_text(hjust = 0.5))

point_RK4_acc_April <- ggplot() +
  geom_polygon(data = south_africa_coast_hi_res, aes(x = lon, y = lat, group = PID),
               size = 1.0, colour = "black", fill = NA) +
  geom_point(data = pass_acc_April, aes(x = lon, y = lat, colour = distance)) +
  coord_cartesian(xlim = c(14, 20), ylim = c(-35, -30)) +
  xlab("Longtitude") +
  ylab("Latitude") +
  ggtitle("") +
  guides(fill=guide_legend(title="Number of particles")) +
  coord_fixed(ratio=1/1) + # fix the aspect ratio of plot
  theme_bw() +
  theme(plot.title = element_text(hjust = 0.5))

point_kelp_acc_April <- ggplot() +
  geom_polygon(data = south_africa_coast_hi_res, aes(x = lon, y = lat, group = PID),
               size = 1.0, colour = "black", fill = NA) +
  geom_point(data = kelp_acc_April, aes(x = lon, y = lat, colour = age)) +
  #scale_fill_continuous(type = "viridis", limits = c(0, 30)) +
  coord_cartesian(xlim = c(14, 20), ylim = c(-35, -30)) +
  xlab("Longtitude") +
  ylab("Latitude") +
  ggtitle("") +
  guides(fill=guide_legend(title="Age")) +
  coord_fixed(ratio=1/1) + # fix the aspect ratio of plot
  theme_bw() +
  theme(plot.title = element_text(hjust = 0.5))

@@

heatmap_RK4_acc_July <- ggplot() +
  geom_polygon(data = south_africa_coast_hi_res, aes(x = lon, y = lat, group = PID),
               size = 1.0, colour = "black", fill = NA) +
  #geom_bin2d(data = p_RK4, bins = 80, aes(x = lon, y = lat)) +
  geom_hex(data = pass_acc_July, bins = 80, aes(x = lon, y = lat), legend = FALSE) +  scale_fill_continuous(type = "viridis", limits = c(1, 720)) +
  geom_path(data = pass_acc_mean_July,aes(x = lon, y = lat, color = 'red'), show.legend = FALSE) +
  coord_cartesian(xlim = c(14, 20), ylim = c(-35, -30)) +
  xlab("Longtitude") +
  ylab("Latitude") +
  ggtitle("Passive particles") +
  guides(fill=guide_legend(title="Number of particles")) +
  coord_fixed(ratio=1/1) + # fix the aspect ratio of plot
  theme_bw() +
  theme(plot.title = element_text(hjust = 0.5))

heatmap_kelp_acc_July <- ggplot() +
  geom_polygon(data = south_africa_coast_hi_res, aes(x = lon, y = lat, group = PID),
               size = 1.0, colour = "black", fill = NA) +
  #geom_bin2d(data = p_RK4, bins = 80, aes(x = lon, y = lat)) +
  geom_hex(data = kelp_acc_July, bins = 80, aes(x = lon, y = lat), legend = FALSE) +  scale_fill_continuous(type = "viridis", limits = c(1, 720)) +
  geom_path(data = kelp_acc_mean_July,aes(x = lon, y = lat, color = 'red'), show.legend = FALSE) +
  coord_cartesian(xlim = c(14, 20), ylim = c(-35, -30)) +
  xlab("Longtitude") +
  ylab("Latitude") +
  ggtitle("Kelp particles") +
  guides(fill=guide_legend(title="Number of particles")) +
  coord_fixed(ratio=1/1) + # fix the aspect ratio of plot
  theme_bw() +
  theme(plot.title = element_text(hjust = 0.5))

point_RK4_acc_July <- ggplot() +
  geom_polygon(data = south_africa_coast_hi_res, aes(x = lon, y = lat, group = PID),
               size = 1.0, colour = "black", fill = NA) +
  geom_point(data = pass_acc_July, aes(x = lon, y = lat, colour = distance)) +
  coord_cartesian(xlim = c(14, 20), ylim = c(-35, -30)) +
  xlab("Longtitude") +
  ylab("Latitude") +
  ggtitle("") +
  guides(fill=guide_legend(title="Number of particles")) +
  coord_fixed(ratio=1/1) + # fix the aspect ratio of plot
  theme_bw() +
  theme(plot.title = element_text(hjust = 0.5))

point_kelp_acc_July <- ggplot() +
  geom_polygon(data = south_africa_coast_hi_res, aes(x = lon, y = lat, group = PID),
               size = 1.0, colour = "black", fill = NA) +
  geom_point(data = kelp_acc_July, aes(x = lon, y = lat, colour = age)) +
  #scale_fill_continuous(type = "viridis", limits = c(0, 30)) +
  coord_cartesian(xlim = c(14, 20), ylim = c(-35, -30)) +
  xlab("Longtitude") +
  ylab("Latitude") +
  ggtitle("") +
  guides(fill=guide_legend(title="Age")) +
  coord_fixed(ratio=1/1) + # fix the aspect ratio of plot
  theme_bw() +
  theme(plot.title = element_text(hjust = 0.5))

>>>>

---
title: 'Numerical experiment investigating the influence of drag on trajectory patterns of floating macroalgae'
author: 
- R Coppin^[Department of Biodiversity and Conservation Biology, University of the Western Cape, Private Bag X17, Bellville 7535, South Africa], C Rautenbach^[National Institute of Water and Atmospheric Research, 41 Market Place Viaduct Harbour, 1010 Auckland, Private Bag 99940, Newmarket, Auckland 1149, New Zealand], AJ Smit^[South African Environmental Observation Network, Elwandle Coastal Node, Port Elizabeth, South Africa]
output:
  word_document:
    reference_docx: markdown/wiley_template.docx
  pdf_document:
    fig_caption: yes
    latex_engine: xelatex
  html_document:
bibliography: references.bib
csl: markdown/apa.csl.txt
abstract: "**Abstract**: Ocean currents act as an important dispersal mechanism of material on the ocean surface, both natural and anthropogenic. Macroalgae are one of the most important natural dispersal vectors and are regarded as the 'tumble-weed' of the ocean. Despite many studies that exist on the topic, the relative role of wind and surface currents in influencing the trajectory of macroalgal dispersal is still unknown. Past studies focus on kelp-rafts, which can vary greatly in size, making it difficult to form a consenses as to the relative role of wind versus surface currents. In addition, past studies have not considered surface-area in relation to drag characteristics of floating macroalgae, both of which have been shown to play a role in the trajectory and accumulation of other flotsam. Advances in Lagrangian trajectory modeling have been rapid in recent years and allow the use of numerical experiments to investigate trajectories of flotsam in the ocean. This study aimed to shed light on the relative role of wind versus surface currents, and the role of drag in macrolagal trajectory and accumulation. We focused on solitary kelp individuals. This was achieved by comparing simulations of virtual kelp 'particles' which incorporate drag with that of purely Lagrangian particles. The results showed that the virtual kelp particles do follow the ocean currents in general, but that the inclusion of drag into the scenarios causes accumulation in eddys within the study domain. The results also point to the importance of sub-mesoscale features, such as eddys, as important surface accumulation zones for solitary floating macroalage."
---

@@

waterdrag_plot <- ggplot()+
  geom_polygon(data = south_africa_coast_hi_res, aes(x = lon, y = lat, group = PID), size = 1.0, colour = "black",     fill = "grey") +
  coord_cartesian(xlim = c(11, 20), ylim = c(-36, -26)) +
  geom_path(data = total_mean_water, aes(x = lon, y = lat, colour = type))+
  xlab("Longtitude") + 
  ylab("Latitude") + 
  ggtitle("") +
  scale_colour_discrete("Type") +  
  #coord_fixed(ratio=1/1) + # fix the aspect ratio of plot
  theme(plot.title = element_text(hjust = 0.5)) +
  theme_bw()

wwdrag_plot <- ggplot()+
  geom_polygon(data = south_africa_coast_hi_res, aes(x = lon, y = lat, group = PID), size = 1.0, colour = "black",     fill = "grey") +
  coord_cartesian(xlim = c(11, 20), ylim = c(-36, -26)) +
  geom_path(data = total_mean_ww, aes(x = lon, y = lat, colour = type))+
  xlab("Longtitude") + 
  ylab("Latitude") + 
  ggtitle("") +
  scale_colour_discrete("Type") +  
  #coord_fixed(ratio=1/1) + # fix the aspect ratio of plot
  theme(plot.title = element_text(hjust = 0.5)) +
  theme_bw()

@@

waterdrag_plot_April <- ggplot()+
  geom_polygon(data = south_africa_coast_hi_res, aes(x = lon, y = lat, group = PID), size = 1.0, colour = "black",     fill = "grey") +
  coord_cartesian(xlim = c(11, 20), ylim = c(-36, -26)) +
  geom_path(data = total_mean_water_April, aes(x = lon, y = lat, colour = type))+
  xlab("Longtitude") + 
  ylab("Latitude") + 
  ggtitle("") +
  scale_colour_discrete("Type") +  
  #coord_fixed(ratio=1/1) + # fix the aspect ratio of plot
  theme(plot.title = element_text(hjust = 0.5)) +
  theme_bw()

wwdrag_plot_April <- ggplot()+
  geom_polygon(data = south_africa_coast_hi_res, aes(x = lon, y = lat, group = PID), size = 1.0, colour = "black",     fill ="grey") +
  coord_cartesian(xlim = c(11, 20), ylim = c(-36, -26)) +
  geom_path(data = total_mean_ww_April, aes(x = lon, y = lat, colour = type))+
  xlab("Longtitude") + 
  ylab("Latitude") + 
  ggtitle("") +
  scale_colour_discrete("Type") +  
  #coord_fixed(ratio=1/1) + # fix the aspect ratio of plot
  theme(plot.title = element_text(hjust = 0.5)) +
  theme_bw()

@@

waterdrag_plot_July <- ggplot()+
  geom_polygon(data = south_africa_coast_hi_res, aes(x = lon, y = lat, group = PID), size = 1.0, colour = "black",     fill = "grey") +
  coord_cartesian(xlim = c(11, 20), ylim = c(-36, -26)) +
  geom_path(data = total_mean_water_July, aes(x = lon, y = lat, colour = type))+
  xlab("Longtitude") + 
  ylab("Latitude") + 
  ggtitle("") +
  scale_colour_discrete("Type") + 
  #coord_fixed(ratio=1/1) + # fix the aspect ratio of plot
  theme(plot.title = element_text(hjust = 0.5)) +
  theme_bw()

wwdrag_plot_July <- ggplot()+
  geom_polygon(data = south_africa_coast_hi_res, aes(x = lon, y = lat, group = PID), size = 1.0, colour = "black",     fill = "grey") +
  coord_cartesian(xlim = c(11, 20), ylim = c(-36, -26)) +
  geom_path(data = total_mean_ww_July, aes(x = lon, y = lat, colour = type))+
  xlab("Longtitude") + 
  ylab("Latitude") + 
  ggtitle("") +
  scale_colour_discrete("Type") +  
  #coord_fixed(ratio=1/1) + # fix the aspect ratio of plot
  theme(plot.title = element_text(hjust = 0.5)) +
  theme_bw()

@@

waterdrag_plot_Oct <- ggplot()+
  geom_polygon(data = south_africa_coast_hi_res, aes(x = lon, y = lat, group = PID), size = 1.0,     colour = "black",     fill = "grey") +
  coord_cartesian(xlim = c(11, 20), ylim = c(-36, -26)) +
  geom_path(data = total_mean_water_Oct, aes(x = lon, y = lat, colour = type))+
  xlab("Longtitude") + 
  ylab("Latitude") + 
  ggtitle("") +
  scale_colour_discrete("Type") +  
  theme(plot.title = element_text(hjust = 0.5)) +
  #coord_fixed(ratio=1/1) + # fix the aspect ratio of plot
  theme_bw()

wwdrag_plot_Oct <- ggplot() +
  geom_polygon(data = south_africa_coast_hi_res, aes(x = lon, y = lat, group = PID), size = 1.0,     colour = "black",     fill = "grey") +
  coord_cartesian(xlim = c(11, 20), ylim = c(-36, -26)) +
  geom_path(data = total_mean_ww_Oct, aes(x = lon, y = lat, colour = type))+
  xlab("Longtitude") + 
  ylab("Latitude") + 
  ggtitle("") +
  scale_colour_discrete("Type") +  
  guides(fill=guide_legend(title="Number of particles")) +
  theme(plot.title = element_text(hjust = 0.5)) +
  #coord_fixed(ratio=1/1, clip = "on") + # fix the aspect ratio of plot
  theme_bw()

@@

```{r echo=FALSE, message=FALSE, warning=FALSE, fig.height=12, fig.width=7, fig.cap="Figure 3: Comparison of mean trajectories. Simulations of hydrodynamic drag are presented in Panels A, C, E, G for January, April, July, and October, respectively. Results of simulations including both hydrodynamic drag and wind are in Panels B, D, F, H for January, April, July, and October, respectively. In all panels the passive simulations are represented by black lines."}

@@

heatmap_RK4_acc <- ggplot() +
  geom_polygon(data = south_africa_coast_hi_res, aes(x = lon, y = lat, group = PID),
               size = 1.0, colour = "black", fill = NA) +
  #geom_bin2d(data = p_RK4, bins = 80, aes(x = lon, y = lat)) +
  geom_hex(data = pass_acc, bins = 80, aes(x = lon, y = lat), legend = FALSE) +  scale_fill_continuous(type = "viridis", limits = c(1, 720)) +
  geom_path(data = pass_acc_mean,aes(x = lon, y = lat, color = 'red'), show.legend = FALSE) +
  coord_cartesian(xlim = c(11, 20), ylim = c(-36, -26)) +
  xlab("Longtitude") +
  ylab("Latitude") +
  ggtitle("Passive particles") +
  guides(fill=guide_legend(title="Number of particles")) +
  #coord_fixed(ratio=1/1) + # fix the aspect ratio of plot
  theme_bw() +
  theme(plot.title = element_text(hjust = 0.5))

heatmap_kelp_acc <- ggplot() +
  geom_polygon(data = south_africa_coast_hi_res, aes(x = lon, y = lat, group = PID),
               size = 1.0, colour = "black", fill = NA) +
  #geom_bin2d(data = p_RK4, bins = 80, aes(x = lon, y = lat)) +
  geom_hex(data = kelp_acc, bins = 80, aes(x = lon, y = lat), legend = FALSE) +  scale_fill_continuous(type = "viridis", limits = c(1, 720)) +
  geom_path(data = kelp_acc_mean,aes(x = lon, y = lat, color = 'red'), show.legend = FALSE) +
  coord_cartesian(xlim = c(11, 20), ylim = c(-36, -26)) +
  xlab("Longtitude") +
  ylab("Latitude") +
  ggtitle("Kelp particles") +
  guides(fill=guide_legend(title="Number of particles")) +
  #coord_fixed(ratio=1/1) + # fix the aspect ratio of plot
  theme_bw() +
  theme(plot.title = element_text(hjust = 0.5))

point_RK4_acc <- ggplot() +
  geom_polygon(data = south_africa_coast_hi_res, aes(x = lon, y = lat, group = PID),
               size = 1.0, colour = "black", fill = NA) +
  geom_point(data = pass_acc, aes(x = lon, y = lat, colour = distance)) +
  coord_cartesian(xlim = c(11, 20), ylim = c(-36, -26)) +
  xlab("Longtitude") +
  ylab("Latitude") +
  ggtitle("") +
  guides(fill=guide_legend(title="Number of particles")) +
  #coord_fixed(ratio=1/1) + # fix the aspect ratio of plot
  theme_bw() +
  theme(plot.title = element_text(hjust = 0.5))

point_kelp_acc <- ggplot() +
  geom_polygon(data = south_africa_coast_hi_res, aes(x = lon, y = lat, group = PID),
               size = 1.0, colour = "black", fill = NA) +
  geom_point(data = kelp_acc, aes(x = lon, y = lat, colour = age)) +
  #scale_fill_continuous(type = "viridis", limits = c(0, 30)) +
  coord_cartesian(xlim = c(11, 20), ylim = c(-36, -26)) +
  xlab("Longtitude") +
  ylab("Latitude") +
  ggtitle("") +
  guides(fill=guide_legend(title="Age")) +
  #coord_fixed(ratio=1/1) + # fix the aspect ratio of plot
  theme_bw() +
  theme(plot.title = element_text(hjust = 0.5))

@@

heatmap_RK4_acc_April <- ggplot() +
  geom_polygon(data = south_africa_coast_hi_res, aes(x = lon, y = lat, group = PID),
               size = 1.0, colour = "black", fill = NA) +
  #geom_bin2d(data = p_RK4, bins = 80, aes(x = lon, y = lat)) +
  geom_hex(data = pass_acc_April, bins = 80, aes(x = lon, y = lat), legend = FALSE) +  scale_fill_continuous(type = "viridis", limits = c(1, 720)) +
  geom_path(data = pass_acc_mean_April, aes(x = lon, y = lat, color = 'red'), show.legend = FALSE) +
  coord_cartesian(xlim = c(11, 20), ylim = c(-36, -26)) +
  xlab("Longtitude") +
  ylab("Latitude") +
  ggtitle("Passive particles") +
  guides(fill=guide_legend(title="Number of particles")) +
  #coord_fixed(ratio=1/1) + # fix the aspect ratio of plot
  theme_bw() +
  theme(plot.title = element_text(hjust = 0.5))

heatmap_kelp_acc_April <- ggplot() +
  geom_polygon(data = south_africa_coast_hi_res, aes(x = lon, y = lat, group = PID),
               size = 1.0, colour = "black", fill = NA) +
  #geom_bin2d(data = p_RK4, bins = 80, aes(x = lon, y = lat)) +
  geom_hex(data = kelp_acc_April, bins = 80, aes(x = lon, y = lat), legend = FALSE) +  scale_fill_continuous(type = "viridis", limits = c(1, 720)) +
  geom_path(data = kelp_acc_mean_April,aes(x = lon, y = lat, color = 'red'), show.legend = FALSE) +
  coord_cartesian(xlim = c(11, 20), ylim = c(-36, -26)) +
  xlab("Longtitude") +
  ylab("Latitude") +
  ggtitle("Kelp particles") +
  guides(fill=guide_legend(title="Number of particles")) +
  #coord_fixed(ratio=1/1) + # fix the aspect ratio of plot
  theme_bw() +
  theme(plot.title = element_text(hjust = 0.5))

point_RK4_acc_April <- ggplot() +
  geom_polygon(data = south_africa_coast_hi_res, aes(x = lon, y = lat, group = PID),
               size = 1.0, colour = "black", fill = NA) +
  geom_point(data = pass_acc_April, aes(x = lon, y = lat, colour = distance)) +
  coord_cartesian(xlim = c(11, 20), ylim = c(-36, -26)) +
  xlab("Longtitude") +
  ylab("Latitude") +
  ggtitle("") +
  guides(fill=guide_legend(title="Number of particles")) +
  #coord_fixed(ratio=1/1) + # fix the aspect ratio of plot
  theme_bw() +
  theme(plot.title = element_text(hjust = 0.5))

point_kelp_acc_April <- ggplot() +
  geom_polygon(data = south_africa_coast_hi_res, aes(x = lon, y = lat, group = PID),
               size = 1.0, colour = "black", fill = NA) +
  geom_point(data = kelp_acc_April, aes(x = lon, y = lat, colour = age)) +
  #scale_fill_continuous(type = "viridis", limits = c(0, 30)) +
  coord_cartesian(xlim = c(11, 20), ylim = c(-36, -26)) +
  xlab("Longtitude") +
  ylab("Latitude") +
  ggtitle("") +
  guides(fill=guide_legend(title="Age")) +
  #coord_fixed(ratio=1/1) + # fix the aspect ratio of plot
  theme_bw() +
  theme(plot.title = element_text(hjust = 0.5))

@@

heatmap_RK4_acc_July <- ggplot() +
  geom_polygon(data = south_africa_coast_hi_res, aes(x = lon, y = lat, group = PID),
               size = 1.0, colour = "black", fill = NA) +
  #geom_bin2d(data = p_RK4, bins = 80, aes(x = lon, y = lat)) +
  geom_hex(data = pass_acc_July, bins = 80, aes(x = lon, y = lat), legend = FALSE) +  scale_fill_continuous(type = "viridis", limits = c(1, 720)) +
  geom_path(data = pass_acc_mean_July,aes(x = lon, y = lat, color = 'red'), show.legend = FALSE) +
  coord_cartesian(xlim = c(11, 20), ylim = c(-36, -26)) +
  xlab("Longtitude") +
  ylab("Latitude") +
  ggtitle("Passive particles") +
  guides(fill=guide_legend(title="Number of particles")) +
  #coord_fixed(ratio=1/1) + # fix the aspect ratio of plot
  theme_bw() +
  theme(plot.title = element_text(hjust = 0.5))

heatmap_kelp_acc_July <- ggplot() +
  geom_polygon(data = south_africa_coast_hi_res, aes(x = lon, y = lat, group = PID),
               size = 1.0, colour = "black", fill = NA) +
  #geom_bin2d(data = p_RK4, bins = 80, aes(x = lon, y = lat)) +
  geom_hex(data = kelp_acc_July, bins = 80, aes(x = lon, y = lat), legend = FALSE) +  scale_fill_continuous(type = "viridis", limits = c(1, 720)) +
  geom_path(data = kelp_acc_mean_July,aes(x = lon, y = lat, color = 'red'), show.legend = FALSE) +
  coord_cartesian(xlim = c(11, 20), ylim = c(-36, -26)) +
  xlab("Longtitude") +
  ylab("Latitude") +
  ggtitle("Kelp particles") +
  guides(fill=guide_legend(title="Number of particles")) +
  #coord_fixed(ratio=1/1) + # fix the aspect ratio of plot
  theme_bw() +
  theme(plot.title = element_text(hjust = 0.5))

point_RK4_acc_July <- ggplot() +
  geom_polygon(data = south_africa_coast_hi_res, aes(x = lon, y = lat, group = PID),
               size = 1.0, colour = "black", fill = NA) +
  geom_point(data = pass_acc_July, aes(x = lon, y = lat, colour = distance)) +
  coord_cartesian(xlim = c(11, 20), ylim = c(-36, -26)) +
  xlab("Longtitude") +
  ylab("Latitude") +
  ggtitle("") +
  guides(fill=guide_legend(title="Number of particles")) +
  #coord_fixed(ratio=1/1) + # fix the aspect ratio of plot
  theme_bw() +
  theme(plot.title = element_text(hjust = 0.5))

point_kelp_acc_July <- ggplot() +
  geom_polygon(data = south_africa_coast_hi_res, aes(x = lon, y = lat, group = PID),
               size = 1.0, colour = "black", fill = NA) +
  geom_point(data = kelp_acc_July, aes(x = lon, y = lat, colour = age)) +
  #scale_fill_continuous(type = "viridis", limits = c(0, 30)) +
  coord_cartesian(xlim = c(11, 20), ylim = c(-36, -26)) +
  xlab("Longtitude") +
  ylab("Latitude") +
  ggtitle("") +
  guides(fill=guide_legend(title="Age")) +
  #coord_fixed(ratio=1/1) + # fix the aspect ratio of plot
  theme_bw() +
  theme(plot.title = element_text(hjust = 0.5))
